### 2015-07-07 narrative/intro.tex
Merge branch 'master' of https://bitbucket.org/habbasi/ssio-proposal
Conflicts:
	narrative/intro orig.tex

Avoiding impending bottlenecks in exascale scientific discovery will require
new research into managing, storing and retreiving the large volumes of data that are 
produced by simulations and analyzed for months afterwards.
%
In this project we will demonstrate a cooperative approach for storing data
where the user and the storage system work together to optimize performance with
respect to user requirements, current system state, and characteristics of the tiered-storage system.
Our investigation will include the novel techniques for the efficient mapping of data objects
from the user space across a hierarchical tiered storage. These techniques will
include support for application-guided data reductions with user-defined error bounds
and transformations to optimize performance, capacity and minimize bandwidth bottlenecks.

>>>>

Avoiding impending bottlenecks in exascale scientific discovery will require
new research into managing, storing and retrieving the large volumes of data that are 
produced by simulations and analyzed for months afterwards.
%
In this project we will demonstrate a cooperative approach for storing data
where the user and the storage system work together to optimize performance with
respect to user requirements, current system state, and characteristics of the tiered-storage system.
Our investigation will include the novel techniques for the efficient mapping of data objects
from the user space across a hierarchical tiered storage. These techniques will
include support for application-guided data reductions with user-defined error bounds
and transformations to optimize performance, capacity and minimize bandwidth bottlenecks.
